Kernel k-Groups via Hartigan's Method

### 2018-10-23 energy_clustering/arxiv/energy_clustering.tex
acknowledgements

We would like to thank Carey Priebe for discussions.
We would like to acknowledge the support of the Transformative
Research Award (NIH \#R01NS092474) and  the Defense Advanced Research Projects
Agency’s (DARPA) SIMPLEX program through SPAWAR contract N66001-15-C-4041.

>>>>

We would like to thank Carey Priebe for discussions.
We would like to acknowledge the support of the Transformative
Research Award (NIH \#R01NS092474) and  the Defense Advanced Research Projects
Agency’s (DARPA) SIMPLEX program through SPAWAR contract N66001-15-C-4041,
and also the 
DARPA Lifelong Learning Machines program through contract FA8650-18-2-7834.
